Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-26 LaTeX_paper/paper.tex
add table and graph to paper

% to have more colors avelable
\usepackage{xcolor}

@@

@@

\subsection{Comparing the sides}\label{document:my_comparator}
The last step needed before it is possible to start working on
a solver algorithm, is to compare the sides that have been
generated by the previous step.\newline
In order to generate a compatibility shore,
the program compute the following steps:

@@

\section{Apling already existing algorithm to the real world}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.
\newline \newline
The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

@@

  \item \textbf{corruption rate:}\newline
\end{itemize}

>>>>

@@

% for the table
\usepackage[table,xcdraw]{xcolor}

% to include svg images
\usepackage{svg}

@@

\subsection{Comparing The Sides}\label{document:my_comparator}
The last step needed before it is possible to start working on
a solver algorithm, is to compare the sides that have been
generated by the previous step.\newline
In order to generate a compatibility shore,
the program compute the following steps:

@@

\section{Apling Already Existing Algorithms To The Real World}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.
\newline \newline
The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

@@

  \item \textbf{corruption rate:}\newline
  Is defined as: \(1-\sqrt{c.c \: match\%}\). ideally this should be 0.

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{FFE599}}c 
  >{\columncolor[HTML]{B6D7A8}}c 
  >{\columncolor[HTML]{9FC5E8}}c 
  >{\columncolor[HTML]{F9CB9C}}c 
  >{\columncolor[HTML]{D9D2E9}}c }
  \cline{1-1}
  \multicolumn{1}{|c|}{\cellcolor[HTML]{F1C232}threshold} &
    \cellcolor[HTML]{6AA84F}match\% &
    \cellcolor[HTML]{3C78D8}c.c match\% &
    \cellcolor[HTML]{E69138}limit match\% &
    \cellcolor[HTML]{8E7CC3}corruption rate \\ \cline{1-1}
  0.000 & 1.000 & 1.000 & 0.984 & 0.000 \\
  0.025 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.050 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.075 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.100 & 0.408 & 1.000 & 0.392 & 0.000 \\
  0.125 & 0.406 & 1.000 & 0.391 & 0.000 \\
  0.150 & 0.400 & 1.000 & 0.385 & 0.000 \\
  0.175 & 0.386 & 1.000 & 0.371 & 0.000 \\
  0.200 & 0.364 & 1.000 & 0.348 & 0.000 \\
  0.225 & 0.335 & 1.000 & 0.319 & 0.000 \\
  0.250 & 0.298 & 1.000 & 0.282 & 0.000 \\
  0.275 & 0.253 & 1.000 & 0.237 & 0.000 \\
  0.300 & 0.201 & 1.000 & 0.185 & 0.000 \\
  0.325 & 0.158 & 1.000 & 0.142 & 0.000 \\
  0.350 & 0.125 & 0.944 & 0.110 & 0.028 \\
  0.375 & 0.100 & 0.944 & 0.085 & 0.028 \\
  0.400 & 0.080 & 0.944 & 0.065 & 0.028 \\
  \cellcolor[HTML]{FF0000}0.425 &
    \cellcolor[HTML]{FF0000}0.054 &
    \cellcolor[HTML]{FF0000}0.889 &
    \cellcolor[HTML]{FF0000}0.040 &
    \cellcolor[HTML]{FF0000}0.057 \\
  0.450 & 0.043 & 0.889 & 0.029 & 0.057 \\
  0.475 & 0.034 & 0.778 & 0.022 & 0.118 \\
  0.500 & 0.025 & 0.778 & 0.013 & 0.118 \\
  0.525 & 0.023 & 0.778 & 0.010 & 0.118 \\
  0.550 & 0.020 & 0.667 & 0.010 & 0.184 \\
  0.575 & 0.019 & 0.667 & 0.009 & 0.184 \\
  0.600 & 0.016 & 0.556 & 0.007 & 0.255 \\
  0.625 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.650 & 0.014 & 0.556 & 0.005 & 0.255 \\
  0.675 & 0.006 & 0.222 & 0.003 & 0.529 \\
  0.700 & 0.003 & 0.111 & 0.001 & 0.667 \\
  0.725 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.750 & 0.001 & 0.000 & 0.001 & 1.000 \\
  0.775 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.800 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.825 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.850 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.875 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.900 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.925 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.950 & 0.000 & 0.000 & 0.000 & 1.000 \\
  0.975 & 0.000 & 0.000 & 0.000 & 1.000 \\
  1.000 & 0.000 & 0.000 & 0.000 & 1.000
  \end{tabular}
  \end{table}

\centering
\includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
